%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%





% Inbuilt themes in beamer
\documentclass{beamer}
% Theme choice:
\usetheme{CambridgeUS}
% Title page details: 
\title{Assignment-6} 
\author{K Vivek Kumar - CS21BTECH11026}
\date{\today}
\logo{\large \LaTeX{}}


\begin{document}

% Title page frame
\begin{frame}
    \titlepage 
\end{frame}

% Remove logo from the next slides
\logo{}


% Outline frame
\begin{frame}{Class-12-Probability-Exercise-13.4}
TABLE of CONTENTS
    \tableofcontents
\end{frame}


% Lists frame
\section{Question}
\begin{frame}{Problem 1}
State which of the following are not the probability distributions of a random variable. Give reasons for your answer.
\begin{itemize}
    \item
    \begin{tabular}{|c|c|c|c|}
\hline
    X & 0 & 1 & 2 \\ 
\hline
    P(X) & 0.4 & 0.4 & 0.2\\ 
\hline
\end{tabular}

    \item \begin{tabular}{|c|c|c|c|c|c|}
\hline
    X & 0 & 1 & 2 & 3 & 4 \\ 
\hline
    P(X) & 0.1 & 0.5 & 0.2 & -0.1 & 0.3\\ 
\hline
\end{tabular}
\item \begin{tabular}{|c|c|c|c|}
\hline
    Y & -1 & 0 & 1 \\ 
\hline
    P(Y) & 0.6 & 0.1 & 0.2\\ 
\hline
\end{tabular}
\item \begin{tabular}{|c|c|c|c|c|c|}
\hline
    Z & 3 & 2 & 1 & 0 & -1 \\ 
\hline
    P(Z) & 0.3 & 0.2 & 0.4 & 0.1 & 0.05\\ 
\hline
\end{tabular}
    \end{itemize}
\end{frame}


% Blocks frame
\section{Solution : Properties involved}
\begin{frame}{Solution}
We can verify whether a probability distribution is valid for a given random variable by checking two of its properties. The below are the one to be verified in each case for a random variable X.\\
\begin{block}{Property-1}
        The value of P(X) should always be positive.
\begin{align*}
p_i>0, \text{for $i = {1,2,3,...,n}$}
\end{align*}
    \end{block}
    \begin{block}{Property-2}
       The sum of all the values of P(X) should always sum upto one.
\begin{align*}
\sum^{n}_{i = 1}p_i = 1, \text{for $i = {1,2,3,...,n}$}
\end{align*}
    \end{block}
\end{frame} 
\section{Solution (i)}
\begin{frame}{Solution (i)}
(i) Random variable : X
\begin{table}
\centering

\begin{tabular}{|c|c|c|c|}
\hline
    X & 0 & 1 & 2 \\ 
\hline
    P(X) & 0.4 & 0.4 & 0.2\\ 
\hline
\end{tabular}\\
\end{table}
\par For the random variable X, we can observe that all the $p_i$ are positive, and also
    \begin{align}
    p_1 + p_2 + p_3 &= 0.4 + 0.4 + 0.2\\ 
   p_1 + p_2 + p_3 &= 1
    \end{align}
    $\therefore$ This probability distribution of the random variable X is a valid one.
\end{frame} 
\section{Solution (ii)}
\begin{frame}{Solution (ii)}
(ii) Random variable : X
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
    X & 0 & 1 & 2 & 3 & 4 \\ 
\hline
    P(X) & 0.1 & 0.5 & 0.2 & -0.1 & 0.3\\ 
\hline
\end{tabular}\\
\end{table}
\par For this probability distribution we can observe that the value of $p_4$ i.e., -0.1 is a negative value, which violates the first property of a probability distribution.\\
	      $\therefore$ This probability distribution of the random variable X is \textbf{NOT} a valid one.
\end{frame}
\section{Solution (iii)}
\begin{frame}{Solution (iii)}
(iii) Random variable : Y
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
    Y & -1 & 0 & 1 \\ 
\hline
    P(Y) & 0.6 & 0.1 & 0.2\\ 
\hline
\end{tabular}\\
\end{table}
\par For the random variable Y, we can observe that all the $p_i$ are positive, and also
	      \begin{align}
	      p_1 + p_2 + p_3 &= 0.6 + 0.1 + 0.2\\
	       p_1 + p_2 + p_3 &= 0.9 < 1
	      \end{align}
	      Though the property 1 is valid here, but the property 2 isn't a valid one. The sum is not coming out to be 1.\\
	      $\therefore$ This probability distribution of the random variable Y is \textbf{NOT} a valid one.
\end{frame}
\section{Solution (iv)}
\begin{frame}{Solution (iv)}
(iv) Random variable : Z
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
    Z & 3 & 2 & 1 & 0 & -1 \\ 
\hline
    P(Z) & 0.3 & 0.2 & 0.4 & 0.1 & 0.05\\ 
\hline
\end{tabular}\\
\end{table}
\par For the random variable Z, we can observe that all the $p_i$ are positive, and also
 \begin{align}
 \begin{split}
p_1 + p_2 + p_3 + p_4 + p_5 ={}& 0.3 + 0.2 + 0.4 \\
                               &+ 0.1 + 0.05
 \end{split}\\
p_1 + p_2 + p_3 + p_4 + p_5 ={}& 1.05 > 1
 \end{align}
	      Though the property 1 is valid here, but the property 2 isn't a valid one. The sum is not coming out to be 1.\\
	      $\therefore$ This probability distribution of the random variable Z is \textbf{NOT} a valid one.
\end{frame}
\end{document}